---
title: "Zombie Homework Problem Week 4"
author: "Brandon Güell"
date: "9/26/2017"
output: html_document
---

```{r}
library(curl)
f <- f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall17/zombies.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```
#1
Calculate the population mean and standard deviation for each quantitative random variable (height, weight, age, number of zombies killed, and years of education). NOTE: You will not want to use the built in  var() and sd() commands as these are for samples.

so we know this is a population, not a sample. I think the means are the same for a pop and sample so lets start with that
```{r}
library(dplyr)
mean_of_variables<-d %>%
summarise(mean(height), mean(weight), mean(age), mean(zombies_killed), mean(years_of_education))
mean_of_variables

#standard deviation for pop== sqrt(sum((x - mean(x))^2)/length(x))
#lets create a function so that we dont have to type it out for each one! lol maybe!
#awesome i found it in module 7!!! here it is, first the variance then the sd of a pop
pop_v <- function(x) {sum((x - mean(x))^2)/(length(x))}
#create vector of variances
hvar=pop_v(d$height)
wvar=pop_v(d$weight)
avar=pop_v(d$age)
zkvar=pop_v(d$zombies_killed)
yoevar=pop_v(d$years_of_education)
#Just realized after that i dont need these variables LOL... o well

#now the function for sd of a pop
pop_sd <- function(x) {
  sqrt(pop_v(x))}
#then lets run that function on our newly made varaibles
sd_of_variables=c(pop_sd(d$height),pop_sd(d$weight),pop_sd(d$age),pop_sd(d$zombies_killed),pop_sd(d$years_of_education))
sd_of_variables

#okay so finished products are here:

mean_of_variables
sd_of_variables
```
#2
now to plot stuff on ggplot: Use {ggplot} and make boxplots of each of these variables by gender.
```{r}
library(ggplot2)
g= ggplot(data=d, aes(x=gender, y=mean_of_variables)) + geom_boxplot()
g

```
#3
Scatterplots:Use {ggplot} and make scatterplots of height and weight in relation to age. Do these variables seem to be related? In what way?
```{r}
g= ggplot(data=d, aes(x=age, y=height)) + geom_point() + geom_smooth()
g
#height seems to increase with age: positive correlation... you can see it nicely here also:
g= ggplot(data=d, aes(x=age, y=height)) + geom_point() + geom_smooth(method = "lm")
g

g= ggplot(data=d, aes(x=age, y=weight)) + geom_point() + geom_smooth()
g
#weight seems to be less strongly correlated with age, but still a positive correlation
g= ggplot(data=d, aes(x=age, y=weight)) + geom_point() + geom_smooth(method = "lm")
g

#so they are related because as age increases, they both increase?... makes logical sense also
```

#4
Using histograms and Q-Q plots, check whether the quantitative variables seem to be drawn from a normal distribution. Which seem to be and which do not (hint: not all are drawn from the normal distribution)? For those that are not, can you determine what common distribution they are drawn from?

```{r}
#lets start with height...
hist(d$height) #seems super normal to me... lets check with Q-Q
qqnorm(d$height, main = "Normal QQ plot random normal variables") #yup seems normal

#weight
hist(d$weight) #hmm less perfectly normal than before but i think it counts! lets check!
qqnorm(d$weight, main = "Normal QQ plot random normal variables") #yup seems normal

#age
hist(d$age) #looks normal
qqnorm(d$age, main = "Normal QQ plot random normal variables") #yup seems normal again

#zombies killed
hist(d$zombies_killed) #definitely NOT normal... I'd guess Poisson dist. or geometric?
qqnorm(d$zombies_killed, main = "Normal QQ plot random normal variables") #definitely NOT normal

#years of education
hist(d$years_of_education) #again definitely NOT normal...  Poisson dist. or geometric? again
qqnorm(d$years_of_education, main = "Normal QQ plot random normal variables") #definitely NOT normal

```

#5
Now use the sample() function to sample ONE subset of 30 zombie survivors (without replacement) from this population and calculate the mean and sample standard deviation for each variable. Also estimate the standard error for each variable and construct the 95% confidence interval for each mean. Note that for the variables that are not drawn from the normal distribution, you will need to base your estimate of the CIs on some different distribution

```{r}
#had to look this up... dplyr has a nice function lets use it
library(dplyr)
sample1=sample_n(d, size=30, replace = FALSE) # BOOYAA worked! oh shit its not hte sample() function though... lol o well this was easier?!
sample1

mean_of_sample_variables<-sample1 %>%
summarise(mean(height), mean(weight), mean(age), mean(zombies_killed), mean(years_of_education))
mean_of_sample_variables

#now we can do the sd() function. YAY that is easier... here it is

sd_of_sample_variables<-sample1 %>%
summarise(sd(height), sd(weight), sd(age), sd(zombies_killed), sd(years_of_education))
sd_of_sample_variables


#now standard error... i remember seeing a package with se() function.. that is easy lol im going to find it/look it up
library(sciplot)
?se
se_of_sample_variables<-sample1 %>%
summarise(se(height), se(weight), se(age), se(zombies_killed), se(years_of_education))
se_of_sample_variables
#nice! I assume this works for this sample becasue i called it from sample1 which is a sample already???

#okay now CI of each.. let me find that code!
#so here is code for a generic formula:
normalCI = function(x, CIlevel = 0.95) {
    upper = mean(x) + qnorm(1 - (1 - CIlevel)/2) * sqrt(var(x)/length(x))
    lower = mean(x) + qnorm((1 - CIlevel)/2) * sqrt(var(x)/length(x))
    ci <- c(lower, upper)
    return(ci)
}
hCI=normalCI(sample1$height, 0.95)
wCI=normalCI(sample1$weight, 0.95)
aCI=normalCI(sample1$age, 0.95) #sweet!

hCI
wCI
aCI #cool...

normalCI(sample1$zombies_killed, 0.95) # this DOES NOT WORK... not normal...
normalCI(sample1$years_of_education, 0.95)# this DOES NOT WORK... not normal...

#so for those two im guessign we have to bootstrap. here goes nothing, or everything i guess
#An alternative way to calculate a confidence interval is by simulation, which does not presume the underlying distribution from which the random variable is drawn.....== from module so YES lets use bootstrapping

set <- NULL  # sets up a dummy variable to hold our 10000 simulations
n <- 15
for (i in 1:10000) {
    set[i] <- mean(sample(sample1$zombies_killed, n, replace = TRUE))
}
zkCI=quantile(set, c(0.025, 0.975))


#and again for years of education
set <- NULL  
n <- 15
for (i in 1:10000) {
    set[i] <- mean(sample(sample1$years_of_education, n, replace = TRUE))
}
yoeCI=quantile(set, c(0.025, 0.975))

#so here they are:
zkCI
yoeCI
```

#6
Now draw 99 more random samples of 30 zombie survivors out and calculate the mean for each of the these samples. Together with the first sample you drew out, you now have a set of 100 means for each variable (each based on 30 observations), which constitutes a sampling distribution for each variable. What are the means and standard deviations of this distribution for each variable? How do the standard deviations compare to the standard errors estimated in [5]? What do these sampling distributions look like? Are they normally distributed? What about for those variables that you concluded were not originally drawn from a normal distribution?


```{r}
library(dplyr)
sample2=sample_n(d, size=30)
sample2

```




